### 2017-09-05 Documents/bootcamp_project.tex
Updated Project Guide

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

@@

One of our goals is for you to produce a piece of work you can use
to demonstrate your data and programming skills to potential employers.
That work will come in the form of a Jupyter notebook,
a format that combines code, text, and graphics in one user-friendly document.
We will add them to our GitHub repository so that
you can use a link to show others what you've done.
You will also be able to see what your classmates have done.

@@

\item {\bf Three revised project ideas.}
After giving this more thought, write down three project ideas in (a little) more detail.
{\bf Include likely data sources.}
%Ask questions; we have a lot of experience with this, especially data.
All together this should be roughly one paragraph per idea and one page overall.
Like all work in this course, it should be clean and professional.
%We will keep the copy you hand in to use in class, so keep a separate copy for yourself.

@@

\item {\bf Final project.}
You should submit your {\bf Jupyter notebook\/} to \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
by the due date listed on the course website.
The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
depending on the section you are in.
The file name should be your last names separated by dashes and a short title ---
something like {\tt Jones-Smith-Zhang-India.ipynb}.

@@

@@

\input{../LaTeX/footer.tex}

%\end{document}
\pagebreak
\thispagestyle{empty}
\input{../LaTeX/header.tex}

>>>>

%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../LaTeX/undergrad_preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Project Guide}
\runningheader{}{Data Bootcamp: Project Guide}{}
\runningfooter{}{}{}

\begin{document}

@@

One of our goals is for you to produce a piece of work you can use to demonstrate your data and programming skills to potential employers.
That work will come in the form of a Jupyter notebook,
a format that combines code, text, and graphics in one user-friendly document.
The end product should be posted on your GitHub account in a repository so that
you show others what you've done. You will also be able to see what your classmates have done.

@@

\item {\bf Three revised project ideas.}
After giving this more thought, write down three project ideas in (a little) more detail. {\bf Include likely data sources.}
Ask questions; we have a lot of experience with this, especially data.
All together this should be roughly one paragraph per idea and one page overall. Like all work in this course, it should be clean and professional.
We will keep the copy you hand in to use in class, so keep a separate copy for yourself.

@@

\item {\bf Final project.}
You post your {\bf Jupyter notebook\/} to your GitHub account by the due date listed on the course website. You should create a repository called {\tt Data-Bootcamp-Final-Project} and then post your Jupyter notebook. Exact protocol of naming file will be announced soon.

@@

\newpage

@@

%\input{../LaTeX/footer.tex}

%\end{document}
\pagebreak

%\thispagestyle{empty}
%\input{../LaTeX/header.tex}
